---
title: "Table 1 matches Figure 2!"
author: "Mine Çetinkaya-Rundel"
date: "`r Sys.Date()`"
output: 
  html_document:
    fig_caption: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE)
```

```{r}
library(tidyverse)
conflict_prefer("filter", "dplyr")
library(broom)
library(knitr)
```

In this report we evaluate the relationship between relationship between petal 
length and sepal width for irises.

```{r}
iris_nonsetosa <- iris %>%
  filter(Species != "setosa")
```

The original dataset has `r iris$Species %>% unique() %>% length()` species, but 
we will only work with `r iris_nonsetosa$Species %>% unique() %>% length()` of 
them.

## Model 

The model results are below.

```{r caption = "Table 1"}
m_pl_sw <- lm(Petal.Length ~ Sepal.Width, data = iris_nonsetosa)
tidy_m_pl_sw <- tidy(m_pl_sw)
kable(tidy_m_pl_sw, 
      caption = "Table 1. Regression output for predicting petal length 
      from sepal width.", 
      digits = 2)
```

The slope of the regression model is `r tidy_m_pl_sw %>% filter(term == "Sepal.Width") %>% pull(estimate) %>% round(2)`.

## Visualize

The figure below shows the relationship between these variables, and we observe 
a positive slope in this visualization as well.

```{r fig.cap = "Figure 2. Relationship between petal length and sepal width"}
ggplot(iris_nonsetosa) +
  geom_point(aes(x = Sepal.Width, y = Petal.Length, color = Species)) +
  geom_smooth(aes(x = Sepal.Width, y = Petal.Length), method = "lm") 
```

